\section{Data}
\label{sec:data}

Daily maximum discharge (\textit{Tagesmaxima}) for the Simme at Oberried/Lenk
(BAFU/FOEN station~2219) spans 1974--2025. Combined with \textit{Monatsmaxima} for
1944--1973 from the same station, this yields an extended Annual Maximum Series (AMS)
of $n = 82$ years (1944--2025). The monthly and daily sub-series agree exactly over the
overlap period (maximum difference $= 0.000$\,\si{m^3\per s}), so the two sub-series
are spliced at 1974 without bias. Both records were obtained from the Swiss Federal
Office for the Environment in May 2026.

The supplementary analysis uses daily mean discharge from GRDC station~6935331
(Simme at Lenk, 1944--2020, $n = 77$), providing a 67-year pre-GLOF reference.

GLOF event dates were determined from the Lac des Faverges lake-level time series
provided by \citet{Ogier2021}, who instrumented the lake from 2012 to 2019 at
10-minute resolution (water level, inferred volume, computed discharge). The GLOF date
is defined as the timestamp of peak lake outflow: maximum discharge during the outburst
phase, identified by requiring (i)~lake volume to be decreasing ($\Delta V < 0$) and
(ii)~computed lake discharge to exceed 5\,\si{m^3\per s}. The 2011 event pre-dates the
logger installation and is sourced from cantonal archive records. Uncontrolled outbursts
occurred in each year from 2011 to 2018; from 2019 the bypass channel eliminates
spontaneous outbursts. The eight confirmed event dates are listed in
Table~\ref{tab:glof_dates}.

\begin{table}[H]
  \centering
  \caption{Confirmed GLOF event dates, Plaine Morte glacier (2011--2018). Dates are
           peak lake outflow from the Lac des Faverges time series; 2011 from external
           sources.}
  \label{tab:glof_dates}
  \begin{tabular}{cc}
    \toprule
    Year & GLOF date \\
    \midrule
    2011 & 27 July 2011 \\
    2012 & 16 July 2012 \\
    2013 &  2 August 2013 \\
    2014 &  7 August 2014 \\
    2015 &  1 August 2015 \\
    2016 & 28 August 2016 \\
    2017 & 19 July 2017 \\
    2018 & 27 July 2018 \\
    \bottomrule
  \end{tabular}
\end{table}
