\section{Methods}
\label{sec:methods}

\subsection{Series Construction and GLOF Masking}

Annual block maxima are extracted from the daily discharge record (Module~2, \S4.1).
Three annual maximum series (AMS) are constructed for comparison: (i) the \textbf{full}
1944--2020 series, (ii) a \textbf{GLOF-masked} 1944--2020 series in which discharge
values within $\pm 5$ days of each confirmed GLOF date are set to missing before taking
the block maximum, and (iii) a \textbf{reference} series restricted to the pre-GLOF
period 1944--2010. The five-day window accounts for the typical recession limb of a GLOF
pulse at this gauge and is applied symmetrically to avoid capturing antecedent conditions.

\subsection{GEV Flood Frequency Analysis}

A Generalised Extreme Value (GEV) distribution (Module~2, \S4.2.2) is fitted to each of
the three series by maximum likelihood estimation (MLE). The GEV encompasses the Gumbel
($\xi = 0$), Fréchet ($\xi > 0$), and Weibull ($\xi < 0$) families through its shape
parameter $\xi$, allowing the data to determine the appropriate tail behaviour. Design
quantiles for return periods $T = 2, 5, 10, 20, 50, 100, 200$ years are derived from the
fitted parameters. Confidence intervals on quantile estimates are computed via the delta
method applied to the inverse Fisher information matrix --- a standard approach not
covered in the lecture, which provides CI formulas for the Gumbel case only
(Module~2, Eq.~4.26). Empirical return periods for plotting are assigned using Gringorten
plotting positions (Module~1, Table~3.1). Model fit is compared across series using the
Akaike Information Criterion (Module~2, \S5.5.2).

\subsection{Homogeneity Tests}
\label{sec:methods:tests}

To test H1 and H2, two complementary approaches are applied to the ten 2011--2020
annual maxima, using the pre-GLOF GEV as the null model.

\textbf{Probability Integral Transform and KS test} (Module~1, \S1.3.1, \S3.1.2): each
2011--2020 peak is transformed to a uniform variate via the reference GEV CDF. If the
null holds, these values follow a Uniform(0,1) distribution. Departure is quantified with
the one-sample Kolmogorov--Smirnov statistic, compared against the critical value
$C_\alpha = K_\alpha / (\sqrt{n} + 0.12 + 0.11/\sqrt{n})$ with $K_{0.05} = 1.358$
(Module~1, Eq.~3.3). Tests are run separately for the GLOF-inclusive (Group~A) and
GLOF-masked (Group~B) 2011--2020 peaks. Because the null parameters come from an
independent sample, no Lilliefors correction is needed. Results are visualised with a
probability plot (Module~1, \S3.2).

\textbf{Rank-Sum test} (Module~1, \S2.4.1): a non-parametric test requiring no
distributional assumption. Three pairwise comparisons assess (a) whether GLOF-year full
maxima differ from non-GLOF-year maxima, (b) whether masking restores homogeneity, and
(c) whether the post-2010 non-GLOF regime differs from the pre-GLOF era.
