\section{Conclusion}
\label{sec:conclusion}

This study examines the influence of eight Plaine Morte GLOFs (2011--2018) on flood
frequency statistics at the Simme gauge in Lenk, using daily maximum (BAFU~2219,
1944--2025, $n = 82$) and daily mean discharge (GRDC~6935331, 1944--2020). The key
findings are:

\begin{enumerate}
  \item \textbf{GLOF dominance depends critically on the discharge statistic.}
        Under daily maxima (BAFU~2219), the GLOF produced the annual maximum in 4 of 8
        GLOF years; under daily means (GRDC), in 6 of 8, because sustained outflows
        elevate the daily average above brief storm peaks. The GLOF period also included
        an approximately 127-year natural storm flood (2014) and three 17--20-year events
        (2011, 2015, 2017).

  \item \textbf{One extreme event dominates the signal.}
        The 2018 outburst ($Q = 56.90$\,\si{m^3\per s}, $\hat{T} \approx 789$\,yr)
        drives the KS rejection. After masking, its return period collapses to
        $\hat{T} \approx 1.5$\,yr, confirming the GLOF as the mechanistic cause.

  \item \textbf{Tests reject homogeneity for GLOF-inclusive peaks.}
        KS and Rank-Sum tests reject $H_0$ for Group~A in both datasets
        (BAFU~2219: $p = 0.002$; GRDC: $p < 0.001$). With only $n = 8$ test
        observations, results are sensitive to a single extreme event.

  \item \textbf{Masking restores homogeneity.}
        After the $\pm 5$-day mask, neither test rejects $H_0$ in either dataset
        (BAFU~2219: KS $p = 0.195$, Rank-Sum $p = 0.182$; GRDC: KS $p = 0.321$,
        Rank-Sum $p = 0.226$). The secular-change check (5c) also fails to reject
        (BAFU~2219: $p = 0.172$; GRDC: $p = 0.233$), confirming the natural-flood
        regime is statistically unchanged across the two periods.

  \item \textbf{Design flood inflation is substantial but event-driven.}
        Unmasked GEV fitting overstates the 100-year design quantile by approximately
        15--16\,\% in both datasets, driven by the upward shift in shape parameter
        ($\hat{\xi}: 0.160 \to 0.251$ for BAFU~2219).
\end{enumerate}

For engineering applications, the GLOF-masked or pre-GLOF reference GEV is recommended
as the design distribution for natural flood hazard at Lenk. The 2019 bypass channel
makes this recommendation directly applicable to current planning.
